---
title: "Will Kristin wait for me? - Analysis"
description: |
  Careful analysis done by epic data scientist
author:
  - name: Porter Moody
    url: https://example.com/norajones
date: 06-02-2021
output:
  distill::distill_article:
    self_contained: false
editor_options: 
  chunk_output_type: console
---

Porter will soon be serving a mission and we must calculate the probability of Kristin Durrant waiting for him. please observe.


```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
pacman::p_load(tidyverse, viridis)
theme_set(theme_bw())

dat = tribble(
  ~x,~y,
  "Probability you'll wait for me", 99,
  "Probability you won't", 1
)


ggplot(dat) + aes(x,y) + geom_col(fill = c("blue", "pink"))+
  scale_fill_viridis(discrete=T)+
  labs(title="Important graph")

```




Everyone please observe this telling graph. Kristin's emotions are very constant and are likely to remain constant.

```{r}
f = function(x){2.71^(x-14)}

days = seq(from = 1, to = 16)

fondness1 = c(f(days))
fondness2 = rep(7.344100, 16)

epic = rep("Porter for Kristin", 16)

epic2 = rep("Kristin for Porter", 16)
# direction = c(epic, epic2)
dat = data.frame(weeks = c(days,days),fondness = c(fondness1, fondness2)  ,direction = c(epic,epic2))


# dat = tribble(
#   ~days, ~fondness,~direction,
#   1 , 0, "Porter for Kristin",
#   2 , 1, "Porter for Kristin",
#   3 , 2, "Porter for Kristin",
#   4 , 3, "Porter for Kristin",
#   5 , 4, "Porter for Kristin",
#   6 , 5, "Porter for Kristin",
#   7 , 6, "Porter for Kristin",
#   8 , 7, "Porter for Kristin",
#   9 , 8, "Porter for Kristin",
#   10 , 9, "Porter for Kristin",
#   11 , 10, "Porter for Kristin",
#   12 , 11, "Porter for Kristin",
#   13 , 12, "Porter for Kristin",
#   14 , 13, "Porter for Kristin",
#   15 , 14, "Porter for Kristin",
#   16 , 15, "Porter for Kristin",
#   17 , 16, "Porter for Kristin",
#   18 , 17, "Porter for Kristin",
#   19 , 17, "Porter for Kristin",
#   1 , 100, "Kristin for Porter",
#   2 , 100, "Kristin for Porter",
#   3 , 100, "Kristin for Porter",
#   4 , 100, "Kristin for Porter",
#   5 , 100, "Kristin for Porter",
#   6 , 100, "Kristin for Porter",
#   7 , 100, "Kristin for Porter",
#   8 , 100, "Kristin for Porter",
#   9 , 100, "Kristin for Porter",
#   10 , 100, "Kristin for Porter",
#   11 , 100, "Kristin for Porter",
#   12 , 100, "Kristin for Porter",
#   13 , 100, "Kristin for Porter",
#   14 , 100, "Kristin for Porter",
#   15 , 100, "Kristin for Porter",
#   16 , 100, "Kristin for Porter",
#   17 , 100, "Kristin for Porter",
#   18 , 100, "Kristin for Porter",
#   19 , 100, "Kristin for Porter"
# 
# )
dat = tibble(dat)

ggplot(dat) + aes(weeks, fondness, color = direction) + geom_point() + 
  stat_function(fun = function(x){f(x)})+
  labs(title = "It appears the growth in fondness from Porter to Kristin is exponential.",subtitle = "Currently their fondness levels are equal, but porter's fondness will likely soon reach the skies.")+
  geom_line()



```

We can see this very compelling graph of the correlation between how long we see each other and how excited we are to see each other.
 
```{r}
dat = tribble(
  ~days_without_seeing_each_other,
  40,
  2,
  3,
  4,
  5,
  30,
  7,
  3,
  1,
  .5,
  .5,
  3,
  2
) %>% mutate(excitement = days_without_seeing_each_other*10)

dat %>% ggplot() + aes(days_without_seeing_each_other,excitement) + 
  labs(title = "Correlation between how long Porter and Kristin go without seeing each other and their excitement to see each other",
       subtitle = "R^2 = .99")+
  geom_point(fill = "blue")+
  geom_smooth()
pacman::p_load(pander)

lm(excitement ~ days_without_seeing_each_other  , data= dat) %>% summary() %>% pander()

```





